---
title: "How to use the Googol Game app"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use the Googol Game app}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(GoogolGame)
```

## What is the Googol Game?

The Googol Game is based on the mathematical Secretary Problem. A sequence of
numbers is revealed one at a time. Your goal is to pick the highest number in
the sequence — but once you pass a number, you cannot go back. You win only if
the number you pick turns out to be the highest in the entire sequence,
including numbers you never saw.

## How to launch the app

```{r, eval = FALSE}
run_app()
```

## Step-by-step instructions

### Step 1: Choose a sequence type

When the app opens, choose how to generate the sequence of numbers:

- **Random**: the app generates a sequence of random numbers for you. Enter
  how many cards you want and click **Start game**.
- **Manual**: enter your own numbers one at a time. For each number, type a
  value and optionally select a multiplier (e.g. select `2` and `Googol` to
  enter 2 Googol). Click **Add number** to add another number. You need at 
  least 2 numbers and you can add as many numbers as you want. 
  **Note**: manual entry requires a second person — one who enters the numbers
  and one who plays the game! Hand the keyboard to a friend to enter the 
  numbers and don't peek at the screen ;)

### Step 2: Play the game

After clicking **Start game**, the cards are revealed one at a time:

- Cards you have already seen are shown with their number.
- The current card shows its number and is the one you can pick.
- Cards not yet revealed are shown as `?`.

At each card you have two choices:

- Click **Pick this number** to select the current card as your answer.
- Click **Next** to pass and reveal the next card.

On the last card, only **Pick this number** is available — you must pick.

### Step 3: See the result

After picking, the app shows whether you won or lost:

- **Win**: your chosen number was the highest in the sequence.
- **Loss**: a higher number existed elsewhere in the sequence, along with what
  that number was.

Click **Play again** to return to the setup page and start a new game.
